\assignment

### 2017-03-14 project/paper.rnw
Some plots and equations for the first example.

#library(xtable)
options(xtable.table.placement = 'H', width = 80, scipen = 2,
        show.signif.stars = FALSE)

@@

\textcite{wp,digglebook,baddeleycoeurjolly14,baddeleyturner,diggleetal,bermanturner}

@@

loglinear example from HW4

<<hw4_1>>=
observe_win <- setminus.owin(owin(c(0, 1), c(0, 1)),
                             owin(c(0.5, 0.8), c(0.5, 0.8)))
predict_win <- owin(c(-0.5, 1.5), c(-0.5, 1.5))
hw4 <- rpoispp(function(x, y){exp(5 * x + 2 * y)}, win = observe_win)
par(mar = c(0, 0, 0.5, 0))
plot(hw4)
@

<<hw4_2>>=
hw4_fit <- ppm(hw4, ~ x + y, correction = 'isotropic')
hw4_pred <- predict(hw4_fit, window = predict_win, se = TRUE)
par(mfrow = c(1, 2), mar = c(0, 0, 0.5, 2))
plot(hw4_pred$estimate)
plot(observe_win, add = TRUE, col = '#ffffff40', border = NA)
points(hw4, pch = '.', col = 'white')
plot(hw4_pred$se)
plot(observe_win, add = TRUE, col = '#ffffff40', border = NA)
points(hw4, pch = '.', col = 'white')
@

>>>>

library(xtable)
options(xtable.table.placement = 'H', width = 80, scipen = 2,
        xtable.sanitize.rownames.function = function(x){return(x)},
        show.signif.stars = FALSE)

@@

\textcite{wp,digglebook,bermanturner}

@@

log-linear example from HW4

simulate from
\begin{equation*}
\log(\lambda(x,y)) = 5x + 2y; \quad (x, y) \in (0, 1)^{2}
\end{equation*}
but do not observe any events in \((0.5, 0.8)^{2}\). Then fit
\begin{equation*}
\log(\lambda(x,y)) = \beta_{0} + \beta_{1}x + \beta_{2}y
\end{equation*}
and predict on \((-0.5, 1.5)^{2}\).

<<hw4_sim>>=
observe_win <- setminus.owin(owin(c(0, 1), c(0, 1)),
                             owin(c(0.5, 0.8), c(0.5, 0.8)))
predict_win <- owin(c(-0.5, 1.5), c(-0.5, 1.5))
hw4 <- rpoispp(function(x, y){exp(5 * x + 2 * y)}, win = observe_win)
@

<<hw4_plot, fig.cap = 'One realization of the loglinear intensity on a subset of the unit square.'>>=
par(mar = c(0, 0, 1, 0))
plot(hw4, main = 'Event Locations')
@

<<hw4_fit>>=
hw4_fit <- ppm(hw4, ~ x + y, correction = 'isotropic')
hw4_pred <- predict(hw4_fit, window = predict_win, se = TRUE)
# By default hw4_pred is on a 128 by 128 grid.
@

<<hw4_fitcoefs, results = 'asis'>>=
hw4_coef <- summary(hw4_fit)$coefs.SE.CI[,c('Estimate', 'S.E.')]
rownames(hw4_coef) <- c('\\(\\widehat{\\beta_{0}}\\)',
                        '\\(\\widehat{\\beta_{1}}\\)',
                        '\\(\\widehat{\\beta_{2}}\\)')
xtable(hw4_coef, label = 'hw4est',
       caption = 'Estimated coefficients for the log-linear trend model.')
@

<<hw4_fitplot, fig.cap = 'Estimated log-intensity surface and log-scale prediction standard errors.'>>=
par(mfrow = c(1, 2), mar = c(0, 0, 1.2, 2), las = 2)
plot(log(hw4_pred$estimate), zlim = c(-4.5, 10.5),
     main = expression(log(hat(lambda)(italic(list(x,y))))))
plot(observe_win, add = TRUE, border = '#ffffff40')
points(hw4, pch = '.', col = 'white')
plot(log(hw4_pred$se), zlim = c(-4.5, 10.5),
     main = expression(log(SE(hat(lambda)(italic(list(x,y)))))))
plot(observe_win, add = TRUE, border = '#ffffff40')
points(hw4, pch = '.', col = 'white')
@
